Microplatforms: Product platforms as code

### 2018-03-14 paper.tex
initial bibliography

\usepackage{graphicx}% Include figure files
\usepackage{subcaption}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[british]{babel}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\begin{figure}[b]
        \setlength{\fboxsep}{1em}
        \fbox{
                \begin{minipage}{0.43\textwidth}\raggedright
                        Service name, Programming language(s), Programming paradigm(s), Architectural choices, Integration pattern(s), Transport protocols, Authentication, Authorization, Reporting, ETLs, Databases, Caching, Platform libraries, Service dependencies, CI Pipeline dependencies, 3rd party library dependencies, 3rd party service dependencies, Security threat model, License audit, Compliance audit, Capacity plan, Provisioning plan, Cost reporting plan, Monitoring plan, Maintenance process, Backup and Restore process, Secret management, Secret rotation, On-Call schedule, Configuration management, Workflow management, Alerts, Log aggregation, Unhandled failure aggregation, Operations and incident response runbooks, API documentation, Source Code Repository, Humane Service Registry, Service Discovery Registry, Distributed Tracing Registry, Monitoring Dashboard Registry, Build Artifact Repository, CI pipeline(s): Build, Test, Publish, Integration tests, Contract tests, Canary, Deploy, Post deploy tests. 
                \end{minipage}
                }
                \caption{48 concerns for a single microservice [Sean Treadway, SoundCloud] [https://youtu.be/NX0sHF8ZZgw?t=17m48s]}
        \label{fig:concerns}
\end{figure}

Starting with the software itself, it is crucial that it is thoroughly tested before any part of it can be considered done. Testing is now typically largely automated [https://martinfowler.com/bliki/TestPyramid.html], although manual exploratory testing is also strongly advised [http://www.methodsandtools.com/archive/archive.php?id=65]. Testing activities fit on a scale of the level of integration of all the components involved, from testing each in isolation (e.g. unit testing) to fully integrated testing of the run-time behaviour of the entire application stack.

@@

\bibliography{bibliography}
\bibliographystyle{plain}

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[british]{babel}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\begin{figure}[b]
	\setlength{\fboxsep}{1em}
	\fbox{
		\begin{minipage}{0.43\textwidth}\raggedright
			Service name, Programming language(s), Programming paradigm(s), Architectural choices, Integration pattern(s), Transport protocols, Authentication, Authorization, Reporting, ETLs, Databases, Caching, Platform libraries, Service dependencies, CI Pipeline dependencies, 3rd party library dependencies, 3rd party service dependencies, Security threat model, License audit, Compliance audit, Capacity plan, Provisioning plan, Cost reporting plan, Monitoring plan, Maintenance process, Backup and Restore process, Secret management, Secret rotation, On-Call schedule, Configuration management, Workflow management, Alerts, Log aggregation, Unhandled failure aggregation, Operations and incident response runbooks, API documentation, Source Code Repository, Humane Service Registry, Service Discovery Registry, Distributed Tracing Registry, Monitoring Dashboard Registry, Build Artifact Repository, CI pipeline(s): Build, Test, Publish, Integration tests, Contract tests, Canary, Deploy, Post deploy tests.
		\end{minipage}
	}
	\caption{48 concerns for a single microservice~\cite{Treadway17}}
	\label{fig:concerns}
\end{figure}

Starting with the software itself, it is crucial that it is thoroughly tested before any part of it can be considered done. Testing is now typically largely automated~\cite{FowlerTestPyramid}, although manual exploratory testing is also strongly advised [http://www.methodsandtools.com/archive/archive.php?id=65]. Testing activities fit on a scale of the level of integration of all the components involved, from testing each in isolation (e.g. unit testing) to fully integrated testing of the run-time behaviour of the entire application stack.

@@

\bibliography{bibliography}
\bibliographystyle{apalike}
